How to obtain the redshift distribution from probabilistic redshift estimates

### 2017-06-09 research/paper/draft.tex
wrapping up the outline

@@

@@

\begin{itemize}
	\item Existing methods have shortcomings that propagate to inaccuracies 
in characterizing the cosmological parameters.\\
	\item Photo-$z$ PDFs are probabilistic data products so must be handled 
in a mathematically consistent manner; \chippr is one such method, conditioned 
on some assumptions.
	\item In addition to coming with its own error distribution, the $n(z)$ 
estimator produced by \chippr is more accurate than established estimators; 
furthermore, propagation of the \chippr result leads to a quantifiable 
improvement in the constraints on cosmological parameters.
\end{itemize}

>>>>

I will show that a really wacky interim prior, something very far from the true 
$n(z)$, will imprint itself on the stacked estimator but will have no effect on 
\chippr's result.

@@

I will show that if $n(z)$ has significant features, stacking will not recover 
them but \chippr will.

@@

\begin{itemize}
	\item Existing methods have shortcomings that propagate to inaccuracies 
in characterizing the cosmological parameters.
	\item Photo-$z$ PDFs are probabilistic data products so must be handled 
in a mathematically consistent manner; \chippr is one such method, conditioned 
on some assumptions.
	\item In addition to coming with its own error distribution, the $n(z)$ 
estimator produced by \chippr is more accurate than established estimators; 
furthermore, propagation of the \chippr result leads to a quantifiable 
improvement in the constraints on cosmological parameters.
\end{itemize}
